### 2019-07-17 manuscript/discussion.tex
I think I'm done with everything (through bottom of Discussion). Let me know if I missed anything or left something unclear!

Throughout our numerous model comparisons, we find that inclusion of hidden traits provides a considerably better fit (\cref{supptable:testaddhidden}). 
This is consistent with the expectation that many processes, beyond those associated with the focal traits, can affect inference of speciation and extinction. %removed "one or two" because it's true for N traits.
%A natural follow-up question is, what is this hidden trait?
It is, however, unclear exactly which processes are captured by the hidden traits.
For example, our results show that, to a varying extent, breeding system functions as a hidden trait in the ploidy-centered analysis, and vice versa (\cref{suppfigure:lumpedDP,suppfigure:lumpedIC}).
But the strong statistical support for processes not well explained by ploidy and breeding system (\cref{supptable:testaddhidden}) tempts one to interpret the remaining variation as the effect of other measurable traits.
For example, our data appear to show a rapidly-diversifying Australasian clade of mostly SC species within \emph{Solanum}, which suggests that geography may play a role. % Boris, please check!  Australian?  fixme
Nevertheless, it is also possible that the addition of hidden traits instead explains variation stemming from any of a number of unrelated processes or methodological artifacts, such as variation in rates of molecular evolution or misspecified models of sequence evolution. %Rosana and Emma check me.
%     but don't be circular, test in different clade
% alpha is always low: new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model
%B: this transition from the meaning of hidden states to best practices of lumping is a bit hard.
%Here Rosana adds the value of adding traits with the lumped models
More generally, when analyzing the value of additional traits to a complex model, it may be best to opt for the use of lumped models (\cref{figure:lumped,table:lumped}), and verify that adding a trait is statistically preferred.
In the absence of additional information, the hidden states can be view as a statistical trick, providing an easy way to model extra heterogeneity without directly representing a specific trait.
In our analyses, the transition rates between and within hidden traits did not affect the direction of the net diversification difference. 
We find that it is important to allow for the hidden state transition rates to be asymmetrical, because those models tend to provide a better fit than models that fix the hidden state transition rates to be equal (\cref{suppfigure:asymmetric,supptable:asymmetry}).

@@

Polyploidization is known to be common in plants, but the relative frequency of the reverse process---diploidization---remains unclear, and it is under active investigation \citep{dodsworth_2015,mandakova_2018}.
%
Ignoring diploidization, if it is common, could cause us to both underestimate the polyploidization rate and overestimate of the diploid diversification rate, leading to incorrect conclusions.
Therefore, we included a slate of models with a diploidization parameter, and show that our main conclusions are robust to this process (\cref{suppfigure:alldip}).
These models also suggest modest statistical support for diploidization occurring within Solanaceae (\cref{supptable:testdiploidization}), although our estimates of the diploidization rate were highly uncertain. 
Furthermore, additional lines of evidence for classifying species as diploid or polyploid (beyond the genus-level chromosome multiplicity that we primarily relied on) are needed for more reliable conclusions.
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization might be a potential issue due to ploidy misclassification.  
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.

@@

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% recent work on WGDs conflict with other lines of evidence, especially those concerning the observed simple synteny of genomes in Solanaceae, and patterns of evolution at self-incompatibility loci
%
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \emph{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances is approximately $71 \pm 19$ My \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently diploidized, yielding the widespread and common chromosome numbers in this and related families, n=11--12, presently considered to be diploid \citep{robertson_2011}.

% Part II: evidence against WGD in/near family
On the other hand, there is little evidence for the occurrence of diploidization within Solanaceae itself.
First, the Ks-inferred duplication \citep{tomato2012} likely pre-dates the origin of the family (49 My, HPD 46--53 My; \citealt{sarkinen_2013}). 
Thus, the species in our analyes could be ancestrally polyploid, but would have diploidized before the root of the family.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species. % including all of those in the relatively cytogenetically conserved x=12 group, which includes tomato, potato, eggplant, pepper, and tobacco.
Specifically, chromosome numbers and genome comparisons within the family (esp.\ the x=12 clade containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ by six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca.\ 10 inversions and 11 translocations (likely underestimated).
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
%
% Part IIb: evidence from SI [might need more explaining?]
Furthermore, whole genome duplication in a eudicot lineage ancestral to Solanaceae would clash with the evidence that the homologous mechanism of SI that has been present continually in many families \citep{igic_2006} breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002, mcclure_2009}.
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in Solanaceae and other families if SI was previously broken down by polyploidization.
%
Regardless of whether genome polyploidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that more work is needed for a complete understanding of the joint evolution of ploidy and breeding systems.

>>>>

Throughout our numerous model comparisons, we find that inclusion of hidden traits provides a considerably better fit (\cref{supptable:testaddhidden}). 
This is consistent with the expectation that many processes, beyond those associated with the focal traits, can affect inference of speciation and extinction. %removed "one or two" because it's true for N traits.
%A natural follow-up question is, what is this hidden trait?
It is, however, unclear exactly which processes are captured by the hidden traits.
For example, our results show that, to a varying extent, breeding system functions as a hidden trait in the ploidy-centered analysis, and vice versa (\cref{suppfigure:lumpedDP,suppfigure:lumpedIC}).
But the strong statistical support for processes not well explained by ploidy and breeding system (\cref{supptable:testaddhidden}) tempts one to interpret the remaining variation as the effect of other measurable traits.
For example, our data appear to show a rapidly-diversifying Australasian clade of mostly SC species within \emph{Solanum}, which suggests that geography may play a role. % Boris, please check!  Australian?  fixme
Nevertheless, it is also possible that the addition of hidden traits instead explains variation stemming from any of a number of unrelated processes or methodological artifacts, such as variation in rates of molecular evolution or misspecified models of sequence evolution. %Rosana and Emma check me.
%     but don't be circular, test in different clade
% alpha is always low: new supp fig showing how A & B are inferred on the tree?  at least for ID/CD/CP+A/B model
%B: this transition from the meaning of hidden states to best practices of lumping is a bit hard.
%Here Rosana adds the value of adding traits with the lumped models
More generally, when analyzing the value of additional traits to a complex model, it may be best to opt for the use of lumped models (\cref{figure:lumped,table:lumped}), and verify that adding a trait is statistically preferred.
In the absence of additional information, the hidden states can be viewed as a statistical trick, providing an easy way to model extra heterogeneity without directly representing a specific trait.
In our analyses, the transition rates between and within hidden traits did not affect the direction of the net diversification difference. 
We find that it is important to allow for the hidden state transition rates to be asymmetrical, because those models tend to provide a better fit than models that fix the hidden state transition rates to be equal (\cref{suppfigure:asymmetric,supptable:asymmetry}).

@@

Polyploidization is known to be common in plants, but the relative frequency of the reverse process---diploidization---remains unclear, and it is under active investigation \citep{dodsworth_2015,mandakova_2018}.
%
Ignoring diploidization, if it is common, could cause us to both underestimate the polyploidization rate and overestimate of the diploid diversification rate, leading to incorrect conclusions.
Therefore, we included a slate of models with a diploidization parameter, and show that our main conclusions are robust to this process (\cref{suppfigure:alldip}).
These models also suggest modest statistical support for diploidization (\cref{supptable:testdiploidization}), although our estimates of its rate were highly uncertain. 
Furthermore, additional lines of evidence for classifying species as diploid or polyploid (beyond the genus-level chromosome multiplicity that we primarily relied on) are needed for more reliable conclusions.
%In the cases where ploidy level was assigned by us based chromosome multiplicity at the genus level, estimating diploidization might be a potential issue due to ploidy misclassification.  
%R: By adding diploidization to models of polyploidy linked to diversification it is possible to recover this complicated scenario and to reconcile genomic evidence with comparative phylogenetic models. 
%B: yielding to %R here. I still think there is overwhelming support for this statement, and few of the cited papers show convincingly that, for example, diploidization happens within five orders of magnitude compared with polyploidization, rendering "relatively rare" obsolete or invalid. (P.S. Rare not the same as unimportant!)
%B: was: Diploidization is widely considered to be relatively rare, compared with polyploidization \citep{husband_2013}, but flowering plant lineages are thought to have experienced at least one round of polyploidization in their evolutionary history \citep{soltis_2015}.

@@

Other lines of evidence about the prevalence of diploidization within Solanaceae or its ancestors are mixed or even conflicting.
% Part I: evidence for WGD in/near family
On the one hand, polyploidy may have occurred prior to the origin of Solanaceae, rendering all extant `diploids' secondarily derived.
\Citet{ku2000} and \citet{blanc2004} posited that the lineage leading to tomato, \emph{Solanum lycopersicum}, may have experienced one or more whole genome duplications.
A subsequent analysis of synteny between grape and \emph{Solanum} genomes, as well as the distribution between inferred paralogs within genomes of \emph{Solanum} (tomato and potato) each suggested that this lineage experienced a likely round of ancient genome duplication or triplication \citep{tomato2012}. 
The age of the peak of paralog Ks distances is approximately $71 \pm 19$ My \citep{tomato2012}. 
If this is the case, then all of the genomes may have been subsequently diploidized, yielding the widespread and frequent chromosome numbers in this and closely related families, n=11--12, all presently considered to be diploid \citep{robertson_2011}.

% Part II: evidence against WGD in/near family
On the other hand, there is little evidence for the occurrence of diploidization within Solanaceae itself.
First, the Ks-inferred duplication \citep{tomato2012} likely pre-dates the origin of the family (49 My, HPD 46--53 My; \citealt{sarkinen_2013}). 
Thus, the species in our analyses could be ancestrally polyploid, but would have diploidized before the root of the family.
Second, studies comparing map-based genome synteny within the family find no evidence for recent diploidization \citep{wu_2010a}.
Instead, simple genome re-arrangements appear sufficient to explain chromosomal evolution between a number of species. % including all of those in the relatively cytogenetically conserved x=12 group, which includes tomato, potato, eggplant, pepper, and tobacco.
Specifically, chromosome numbers and genome comparisons within the family (esp.\ the x=12 clade containing \textit{Solanum} and \textit{Nicotiana}) reveal strong conservation.
\citet{wu_2010a} review the evidence from map-based genome comparisons and find that tomato and potato differ by as few as six inversions, tomato and eggplant by 24 inversions and five translocations, tomato and pepper by 19 inversions and six translocations, and tomato and tobacco by ca.\ 10 inversions and 11 translocations.
Recovery of such simple relationships would require outstanding convergent loss of duplicated segments.
%
% Part IIb: evidence from SI [might need more explaining?]
Furthermore, whole genome duplication in a eudicot lineage ancestral to Solanaceae would clash with the evidence that the homologous mechanism of SI, which has been present continually in many families \citep{igic_2006}, breaks down nearly invariably in natural and induced tetraploids \citep{stone_2002, mcclure_2009}.
Most problematically in this context, it is unclear how to explain the maintenance of trans-generic polymorphism at the orthologous S-loci in Solanaceae and other families if SI was previously broken down by polyploidization.
%
Regardless of whether genome polyploidization, followed by widespread diploidization, is a dominant mechanism of genome evolution in Solanaceae, it is clear that more work is needed for a complete understanding of the joint evolution of ploidy and breeding systems.
